TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-11-27 paper/paper.tex
minor change

	In both scenarios the TCP congestion algorithms are tested for multiple characteristics:
	\begin{enumerate}
		\item TCP Window Size measured over time: 
		\item Bandwidth allocation: to determine whether using a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more bandwidth to a TCP transport.
		\item Round Trip Time: to determine the reason of the behaviour of a TCP congestion algorithm in combination with other TCP congestion algorithms.
	\end{enumerate}

>>>>

	In both scenarios the TCP congestion algorithms are tested for multiple characteristics:
	\begin{enumerate}
		\item TCP Window Size measured over time: 
		\item Bandwidth allocation: to determine whether using a specific TCP congestion algorithm in combination with other TCP congestion algorithms results in the allocation of more bandwidth to a specific TCP connection.
		\item Round Trip Time: to determine the reason of the behaviour of a TCP congestion algorithm in combination with other TCP congestion algorithms.
	\end{enumerate}
